Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-08 preliminaries.tex
Remove unused definitions

\subsection{Local Hamiltonian}

The local Hamiltonian problem is defined as follows:

\begin{definition}
	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian. Then $$H=\sum_{j=1}^nH_j$$ is called a \emph{Hamiltonian}.
	If each $H_j$ acts on at most $k$ qubits, then $H$ is called a \emph{$k$-local Hamiltonian}.
\end{definition}

The local Hamiltonian problem is given by let $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, determine whether $\lambda(H)<a$ or $\lambda(H)>b$..

\begin{theorem}
	The Local Hamiltonian problem is QMA-complete.
\end{theorem}

@@

Let $H_1, H_2$ be Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
Then $\exists J\in\mathbb{R}$ s.t.
$\lambda(H_1\big|_S)-\frac{1}{8}\leq
	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.

>>>>

\begin{definition}
	Let $H_1, \ldots, H_n:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitians each acting on at most $k$ qubits, then $$H=\sum_{j=1}^nH_j$$ is called a \emph{$k$-local Hamiltonian}.
\end{definition}

@@

Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$, and $S=\ker H_2$.
Then $\exists J\in\mathbb{R}$ s.t.
$\lambda(H_1\big|_S)-\frac{1}{8}\leq
	\lambda(H_1+JH_2)\leq\lambda(H_1\big|_S)$.
